AppendixVerbTrees.Rmd

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_appendixVerbDomains.Rmd
Init

---
title: "Appendix ICB Corpus Verb Coarsened Meanings"
output: html_document
---

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(tidyverse)
p_load(igraph)
p_load(flextable)
p_load(ftExtra)
p_load(googlesheets4)

@@

```{r, eval=T, echo=F, results="markup", include=T, message=F, cache=F, ft.arraystretch=0.75}

set_flextable_defaults(fonts_ignore=TRUE)

first_two_hops_collapsed_ft <- tree_hypernyms_verbs_used_rooted_table_ready %>%
        ungroup() %>% 
        group_by(level1, level2) %>%
        summarise(level3 = paste0(level3, collapse=" | ")) %>%
        ungroup() %>%
        #dplyr::select(-level2, -level3) %>%
        mutate(level1=level1 %>% str_replace_all("[^A-Za-z0-9 ;]","") %>% str_replace_all("verb","")    ) %>%
        mutate(level2=level2 %>% str_replace_all("[^A-Za-z0-9 ;\\|]","") %>% str_replace_all(";","; ") ) %>%
        mutate(level3=level3 %>% str_replace_all("[^A-Za-z0-9 ;\\|]","")) %>%

        #head(200) %>%
        #dplyr::select(n, lemma, gloss ) %>% #wordnetid
        #mutate(gloss=gloss %>% str_replace_all('[^A-Za-z0-9 ,.]','')) %>%
        dplyr::select(VerbGroup=level1,VerbLevel1=level2,VerbLevel2=level3) %>%
        group_by(VerbGroup) %>%
        flextable::as_flextable() %>%

        #bg( i = which( 1:n_keep %% 2 == 1), part = "body", bg = "#EFEFEF") %>%
        #width(j = 1, width=1.25) %>%
        #width(j = 2:ncol(lit_review_clean), width=0.25) %>%
        flextable::fontsize(size = 6) %>% 
        #rotate(rotation="tbrl",part="header") %>%
        #set_header_labels( values = list(lemma = "lemma", wordnetid = "wordnetid", gloss="gloss", n="uses")) %>%
        #align(align = "center", part = "body") %>%
        #align(align = "center", part = "header") %>%
        flextable::padding(padding = 0, part = "all") %>%
        flextable::line_spacing(space = 1, part = "body") %>%
        #ftExtra::colformat_md(j = 1, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
        #fit_to_width(max_width=12) #This is crazy slow
        #flextable::autofit() 
        #fit_to_width(max_width = 8, max_iter = 40) %>%
        #width(j = 1, width=0.75) %>%
        flextable::width(j = 1, width=1.5) %>%
        flextable::width(j = 2, width=5) #%>%
        #merge_v(j = 1, part = "body", combine = T) #%>%
        #hline(j = 1, border = NULL, part = "body")

@@

first_two_hops_collapsed_ft  %>% saveRDS(here::here(), '/paper/tables/first_two_hops_collapsed_ft.Rds'))
first_two_hops_collapsed_ft

>>>>

---
title: "Appendix Verb Domains"
output: html_document
---

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(tidyverse)
p_load(flextable)
p_load(ftExtra)
p_load(googlesheets4)
library(googlesheets4)

@@

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F}

domains <- verbs_sentence_wordnet_top %>% ungroup() %>%  
            dplyr::select(wordnetid) %>%
            mutate(wordnetid=wordnetid %>% as.character() ) %>% 
            left_join(subject_headings_verbs %>% dplyr::select(wordnetid=a,domain=b)) %>%
            count(domain) %>% 
            arrange(desc(n)) %>% 
            na.omit() %>%
            mutate(perc= round( n/sum(n) * 100 ) ) %>%
  left_join(
    tree_hypernyms_verbs_used_rooted_table_ready %>%
  dplyr::select(level1,level2) %>% distinct() %>% group_by(level1) %>% summarise(level2=level2 %>% paste0(collapse=" | ") ) %>% dplyr::select(domain=level1,Sysnets=level2)
  )

p_load(flextable)
p_load(ftExtra)
set_flextable_defaults(fonts_ignore=TRUE)

domains_ft <- domains %>%
        ungroup() %>% 
        mutate(Sysnets=Sysnets %>% str_replace_all("[^A-Za-z0-9 ;\\|]","")) %>%
        flextable::as_flextable() %>%

        #bg( j = condition, part = "body", bg = "#EFEFEF") %>%
        #width(j = 1, width=1.25) %>%
        #width(j = 2:ncol(lit_review_clean), width=0.25) %>%
        flextable::fontsize(size = 8, part = "body" ) %>% 
        #rotate(rotation="tbrl",part="header") %>%
        set_header_labels( values = list(crisno = "#", input_crisis = "Name", sentence_count="Sentences", word_count="Words", event_count_mean_sum="Events")) %>%
        #align(align = "center", part = "body") %>%
        #align(align = "center", part = "header") %>%
        set_table_properties(layout="autofit") %>%  
        flextable::padding(padding = 0, part = "all") %>%
        flextable::line_spacing(space = 1, part = "body") #%>%
        #ftExtra::colformat_md(j = 1, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above

      #autofit()
      #fit_to_width(max_width=12) #This is crazy slow
      #flextable::autofit() 
      #set_table_properties(width = 1, layout = "autofit")

@@

domains_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/domains_ft.Rds'))
domains_ft

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_appendixVerbMeanings.Rmd
Init

---
title: "Appendix Verb Domains"
output: html_document
---

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(tidyverse)
p_load(flextable)
p_load(ftExtra)
p_load(googlesheets4)
library(googlesheets4)

@@

#wordnet rdf (in tripple format)
fromscratch=F

@@

#wordnet csv
filenames <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/") )
filepaths <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"), full.names = T)

@@

@@

  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds") )

@@

tblg_hypernyms_verbs_used <- g_hypernyms_verbs_used %>% as_tbl_graph()
V(tblg_hypernyms_verbs_used)$lemma <- lemma_df[V(tblg_hypernyms_verbs_used)$name,]$lemma
condition <- V(tblg_hypernyms_verbs_used)$lemma %>% is.na()
V(tblg_hypernyms_verbs_used)$lemma[condition] <- V(tblg_hypernyms_verbs_used)$name[condition]

@@

@@

@@

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F}

domains <- verbs_sentence_wordnet_top %>% ungroup() %>%  
            dplyr::select(wordnetid) %>%
            mutate(wordnetid=wordnetid %>% as.character() ) %>% 
            left_join(subject_headings_verbs %>% dplyr::select(wordnetid=a,domain=b)) %>%
            count(domain) %>% 
            arrange(desc(n)) %>% 
            na.omit() %>%
            mutate(perc= round( n/sum(n) * 100 ) ) %>%
  left_join(
    tree_hypernyms_verbs_used_rooted_table_ready %>%
  dplyr::select(level1,level2) %>% distinct() %>% group_by(level1) %>% summarise(level2=level2 %>% paste0(collapse=" | ") ) %>% dplyr::select(domain=level1,Sysnets=level2)
  )

p_load(flextable)
p_load(ftExtra)
set_flextable_defaults(fonts_ignore=TRUE)

domains_ft <- domains %>%
        ungroup() %>% 
        mutate(Sysnets=Sysnets %>% str_replace_all("[^A-Za-z0-9 ;\\|]","")) %>%
        flextable::as_flextable() %>%

        #bg( j = condition, part = "body", bg = "#EFEFEF") %>%
        #width(j = 1, width=1.25) %>%
        #width(j = 2:ncol(lit_review_clean), width=0.25) %>%
        flextable::fontsize(size = 8, part = "body" ) %>% 
        #rotate(rotation="tbrl",part="header") %>%
        set_header_labels( values = list(crisno = "#", input_crisis = "Name", sentence_count="Sentences", word_count="Words", event_count_mean_sum="Events")) %>%
        #align(align = "center", part = "body") %>%
        #align(align = "center", part = "header") %>%
        set_table_properties(layout="autofit") %>%  
        flextable::padding(padding = 0, part = "all") %>%
        flextable::line_spacing(space = 1, part = "body") #%>%
        #ftExtra::colformat_md(j = 1, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above

      #autofit()
      #fit_to_width(max_width=12) #This is crazy slow
      #flextable::autofit() 
      #set_table_properties(width = 1, layout = "autofit")

@@

domains_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/domains_ft.Rds'))
domains_ft

>>>>

---
title: "Verb Meanings found in the ICB Corpus (top 200)"
output: html_document
---

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(igraph)
p_load(tidyverse)
p_load(flextable)
p_load(ftExtra)
p_load(googlesheets4)
library(googlesheets4)

@@

#wordnet rdf (in tripple format)
#wordnet rdf (in tripple format)
fromscratch=F

@@

#wordnet csv
filenames <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"))
filepaths <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"), full.names = T)

@@

#wordnet_list[[8]]
#wordnet_list[[16]]
#wordnet_list[[19]]

wordnet_list[["wn_cls.csv"]]

wordnet_list[["wn_vgp.csv"]]

@@

  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds"))

@@

tblg_hypernyms_verbs_used <- g_hypernyms_verbs_used %>% as_tbl_graph()
V(tblg_hypernyms_verbs_used)$lemma <- lemma_df[V(tblg_hypernyms_verbs_used)$name,]$lemma
condition <- V(tblg_hypernyms_verbs_used)$lemma %>% is.na()
V(tblg_hypernyms_verbs_used)$lemma[condition] <- V(tblg_hypernyms_verbs_used)$name[condition]
#
library(ggraph)
p <- tblg_hypernyms_verbs_used %>% 
      ggraph(  layout = "sugiyama") + 
      coord_flip() +
      geom_edge_link(width=0.5, alpha=0.25 )  + 
      geom_node_label(aes(label = lemma), repel = TRUE, size=3)

ggsave(filename=paste0(here::here(), "/paper/figures/hypernyms_plot.pdf"), plot=p, height=100,width =32,limitsize = FALSE)

#

@@

library(ggraph)
p_rooted <- tblg_hypernyms_verbs_used_rooted %>% 
            ggraph(  layout = "sugiyama") + 
            coord_flip() +
            geom_edge_elbow(width=0.5, alpha=0.25 )  + 
            geom_node_label(aes(label = lemma), repel = TRUE, size=3)

ggsave(filename=paste0(here::here(), "/paper/figures/hypernyms_rooted_plot.pdf"), plot=p_rooted, height=100,width =32,limitsize = FALSE)

@@

#dendrogram_hypernyms_verbs_used_rooted <- tree_hypernyms_verbs_used_rooted %>% as.dendrogram() #dengraom kills the internal labels and there's a better one anyway
#rn_hypernyms_verbs_used_rooted <- dendrogram_hypernyms_verbs_used_rooted %>% as.radialNetwork()     
#lol <- ToListExplicit(tree_hypernyms_verbs_used_rooted, unname = TRUE) #data.tree will go straight to list https://stackoverflow.com/questions/36273730/turning-relationship-data-into-hierarchical-list-in-r
#d3_dendrogram <- diagonalNetwork(List = lol, fontSize = 8, opacity = 0.9)

#karate_d3 <- igraph_to_networkD3(g_hypernyms_verbs_used_rooted)

#diagonalNetwork(List = karate_d3$links) #, fontSize = 10, opacity = 0.9
#as.radialNetwork(d, root)

#library(dendextend)
#library(ggdendro)
#dendro_hypernyms_verbs_used <- as.dendro(segments=karate_d3$links, labels=karate_d3$nodes, class="hclust")

#dendrogram_hypernyms_verbs_used <- dendro_hypernyms_verbs_used
#attr(dendrogram_hypernyms_verbs_used,"class") <- "dendrogram"
#as.radialNetwork(dendrogram_hypernyms_verbs_used)

## Convert to list format
#Flare <- jsonlite::fromJSON("https://raw.githubusercontent.com/christophergandrud/d3Network/master/JSONdata/flare.json", simplifyDataFrame = FALSE)
#diagonalNetwork(List = Flare) #, fontSize = 10, opacity = 0.9

#require(graphics); require(utils)
#hc <- hclust(dist(USArrests), "ave")
#(dend1 <- as.dendrogram(hc)) # "print()" method

@@

```{r, eval=T, echo=F, results="markup", include=T, message=T, cache=F, ft.arraystretch=0.75}

set_flextable_defaults(fonts_ignore=TRUE)
n_keep=200
verbs_sentence_wordnet_top_ft <-
        verbs_sentence_wordnet_top_unique %>%
        ungroup() %>% 
        head(n_keep) %>%
        dplyr::select(n, lemma, gloss ) %>% #wordnetid
        mutate(gloss=gloss %>% str_replace_all('[^A-Za-z0-9 ,.\"]','')) %>%

        flextable::as_flextable() %>%

        #bg( j = condition, part = "body", bg = "#EFEFEF") %>%
        #width(j = 1, width=1.25) %>%
        #width(j = 2:ncol(lit_review_clean), width=0.25) %>%
        flextable::fontsize(size = 6, part = "all") %>% 
        #rotate(rotation="tbrl",part="header") %>%
        set_header_labels( values = list(lemma = "lemma", wordnetid = "wordnetid", gloss="gloss", n="uses")) %>%
        #align(align = "center", part = "body") %>%
        #align(align = "center", part = "header") %>%
        flextable::padding(padding = 0, part = "all") %>%
        flextable::line_spacing(space = 1, part = "body") %>%
        #ftExtra::colformat_md(j = 1, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
        #fit_to_width(max_width=12) #This is crazy slow
        #flextable::autofit() 
        #set_table_properties(width = 1, layout = "autofit")

      bg( i = which( 1:n_keep %% 2 == 1), part = "body", bg = "#EFEFEF") %>%
      #merge_v(part = "body") %>% 
      flextable::width( j = 1, width=0.3) %>%
      flextable::width( j = 2, width=.75) %>%
      flextable::width( j = 3, width=6) %>%
      #flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
      flextable::padding(padding = 0, part = "body") %>%
      #hline(i=which( actor_agents$Player!=c(actor_agents$Player[2:length(actor_agents$Player)], NA) ), border = fp_border(color="gray", width = 0.25), part = "body")

      #add_header( "IR Player_Pieces"="Citations"

      #            top = TRUE ) %>%
      set_header_labels(
        values = list(
          "uses" = "Count",
          'lemma'='Lemma',
          'gloss'='Gloss'
          ) 
        )

@@

verbs_sentence_wordnet_top_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/verbs_sentence_wordnet_top_ft.Rds'))
verbs_sentence_wordnet_top_ft

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_appendixVerbTrees.Rmd
Init

---
title: "Verb Meanings found in the ICB Corpus (top 200)"
output: html_document
---

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(igraph)
p_load(tidyverse)
p_load(flextable)
p_load(ftExtra)
p_load(googlesheets4)
library(googlesheets4)

```{r}
icb_wide_clean <- readRDS(file=paste0(here::here(), "/data/icb_wide_clean.Rds"))
```

```{r , message=F}

icb_text <- icb_wide_clean %>% dplyr::select(crisno,sentence_number_int_aligned, sentence) %>% distinct() %>% dplyr::mutate_at(vars(sentence_number_int_aligned), as.numeric) %>% arrange(crisno,sentence_number_int_aligned)

# writeLines(icb_text$sentence %>% na.omit() %>% iconv("UTF-8", "ASCII", "?"), paste0(here::here(), "/replication_data/temp/sentences.txt"), useBytes = T)

fromscratch=F
if(fromscratch){

  p_load("spacyr")
  #spacy_install() 
  spacy_initialize(model = "en_core_web_sm")

  parsed <- spacy_parse(icb_text$sentence, nounphrase = TRUE)
  parsed_consolidated <- nounphrase_consolidate(parsed)
  parsed$doc_id_num <- parsed$doc_id %>% str_replace_all("text","") %>% as.numeric()
  parsed$crisno <- icb_text$crisno[parsed$doc_id_num]
  parsed$sentence_number_int_aligned <- icb_text$sentence_number_int_aligned[parsed$doc_id_num]  %>% as.numeric()
  parsed$sentence <- icb_text$sentence[parsed$doc_id_num]

  parsed %>% saveRDS(paste0(here::here(), "/data/parsed.Rds"))

  entities <- entity_extract(parsed, type = "all")
  entities %>% saveRDS(paste0(here::here(), "/data/entities.Rds"))

} else {
  parsed <- readRDS(paste0(here::here(), "/data/parsed.Rds"))
  entities <- readRDS(paste0(here::here(), "/data/entities.Rds"))

entities$doc_id_num <- entities$doc_id %>% str_replace_all("text","") %>% as.numeric()
entities$crisno <- icb_text$crisno[entities$doc_id_num]
entities_unique <- entities %>% dplyr::select(entity,entity_type) %>% mutate(entity = entity %>% str_to_lower() %>% str_replace_all("[^A-Za-z0-9]","") ) %>% distinct()

target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")

unique_agent_q_codes <- dictionary_actors$value_disaggregated_wikidata_id %>% na.omit() %>% unique() %>% str_split(";") %>% unlist() %>% trimws() %>% unique()
unique_actor_q_codes <- dictionary_actors$value_normalized_wikidata_id %>% na.omit() %>% unique() %>% str_split(";") %>% unlist() %>% trimws() %>% unique()

verbs_sentence <- parsed %>% filter(pos=="VERB")

verbs <- parsed %>% filter(pos=="VERB") %>% dplyr::select(lemma, pos) %>% distinct()

entities_per_sentence <- entities %>% 
  count(doc_id) %>% 
  summarise(
    entities_per_sentence_min=min(n),
    entities_per_sentence_mean=mean(n),
    entities_per_sentence_max=max(n),
  )

```{r, messages=F, results='hide', warnings=F, include=FALSE}

#wordnet rdf (in tripple format)
#wordnet rdf (in tripple format)
fromscratch=F

wordnet_rdf <- readRDS(paste0(here::here(), "/replication_data/in/wordnet_rdf.Rds") )

subject_headings <- wordnet_rdf %>% as_tibble() %>% filter(value %>% str_detect('http://purl.org/dc/terms/subject'))
subject_headings_verbs <- subject_headings %>%
                          filter(value %>% str_detect('-v>')) %>% 
                          mutate(value=value %>% str_replace("<http://wordnet-rdf.princeton.edu/id/","2")) %>% 
                          mutate(value=value %>% str_replace("-v> <http://purl.org/dc/terms/subject> ","\t")) %>%
                          separate(value, c("a", "b"), extra = "drop", fill = "right", sep="\t") %>%
                          mutate(b = b %>% str_replace_all('\\"| \\.',""))

#subject_headings <- wordnet_rdf %>% as_tibble() %>% filter(value %>% str_detect('00002137')) #the first digit is for part of speech so we can remove that if we subset to just verbs

#wordnet csv
filenames <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"))
filepaths <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"), full.names = T)

wordnet_list <- lapply(filepaths, read_csv, col_names=F, progress=F, show_col_types=F)
names(wordnet_list) <- filenames

#wordnet_list[[8]]
#wordnet_list[[16]]
#wordnet_list[[19]]

wordnet_list[["wn_cls.csv"]]

wordnet_list[["wn_vgp.csv"]]

hypernyms <- wordnet_list[['wn_hyp.csv']] %>% 
              dplyr::select(a=X1,b=X2) %>% 
              left_join(wordnet_list[["wn_s.csv"]] %>% dplyr::select(a=X1, a_lemma=X3) ) %>% 
              left_join(wordnet_list[["wn_s.csv"]] %>% dplyr::select(b=X1, b_lemma=X3) )

library(igraph)
g_hypernyms <-  graph_from_data_frame(hypernyms, directed = TRUE)

wordnet <- wordnet_list[["wn_s.csv"]] %>% dplyr::select(wordnetid=X1, lemma=X3, tense=X4) %>% full_join( wordnet_list[['wn_g.csv']] %>% dplyr::select(wordnetid=X1, gloss=X2) )

wordnet_verbs <- wordnet %>% filter(tense=='v')

verbs_sentence_wordnet <- verbs_sentence %>% left_join(wordnet_verbs)
#dim(verbs_sentence_wordnet) #227,426

#I think we use sbert to embed the original sentence and the gloss and then calculate pairwise distances

```{r, echo=F, messages=F, warnings=F, results='hide'}

@@

  #Isn't it just one minus the other?
  verbs_sentence_wordnet$distances <- rowSums((glosses_embeddings_expanded-sentences_embeddings_expanded)^2)
  verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds"))

@@

  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds"))

@@

ggsave(filename=paste0(here::here(), "/paper/figures/hypernyms_plot.pdf"), plot=p, height=100,width =32,limitsize = FALSE)

@@

ggsave(filename=paste0(here::here(), "/paper/figures/hypernyms_rooted_plot.pdf"), plot=p_rooted, height=100,width =32,limitsize = FALSE)

library(data.tree)
library(networkD3) 
df_hypernyms_verbs_used_rooted <- g_hypernyms_verbs_used_rooted %>% as_edgelist( names = TRUE) %>% as.data.frame()
df_hypernyms_verbs_used_rooted_labeled <- df_hypernyms_verbs_used_rooted %>% as_tibble() %>% 
                                          left_join(lemma_df %>% rename(V1=name, lemma1=lemma)) %>%
                                          left_join(lemma_df %>% rename(V2=name, lemma2=lemma)) %>%
                                          mutate(lemma1=ifelse(is.na(lemma1), V1, lemma1)) %>%
                                          mutate(lemma2=ifelse(is.na(lemma2), V2, lemma2)) #%>%
                                          #dplyr::select(lemma1,lemma2)

library("dendextend")

tree_hypernyms_verbs_used_rooted <- df_hypernyms_verbs_used_rooted_labeled %>% as.Node(mode="network")
tree_hypernyms_verbs_used_rooted_table <- tree_hypernyms_verbs_used_rooted %>% ToDataFrameTypeCol()

tree_hypernyms_verbs_used_rooted_table_ready <- 
                                            tree_hypernyms_verbs_used_rooted_table %>% 
                                                                      left_join(lemma_df %>% dplyr::rename(level_3=name, lemma3=lemma)) %>% 
                                                                      left_join(lemma_df %>% dplyr::rename(level_4=name, lemma4=lemma)) %>%
                                                                      dplyr::select(level1=level_2, level2=lemma3, level3=lemma4) %>%
                                                                      arrange(level1,level2,level3) %>% distinct()

#dendrogram_hypernyms_verbs_used_rooted <- tree_hypernyms_verbs_used_rooted %>% as.dendrogram() #dengraom kills the internal labels and there's a better one anyway
#rn_hypernyms_verbs_used_rooted <- dendrogram_hypernyms_verbs_used_rooted %>% as.radialNetwork()     
#lol <- ToListExplicit(tree_hypernyms_verbs_used_rooted, unname = TRUE) #data.tree will go straight to list https://stackoverflow.com/questions/36273730/turning-relationship-data-into-hierarchical-list-in-r
#d3_dendrogram <- diagonalNetwork(List = lol, fontSize = 8, opacity = 0.9)

#karate_d3 <- igraph_to_networkD3(g_hypernyms_verbs_used_rooted)

#diagonalNetwork(List = karate_d3$links) #, fontSize = 10, opacity = 0.9
#as.radialNetwork(d, root)

#library(dendextend)
#library(ggdendro)
#dendro_hypernyms_verbs_used <- as.dendro(segments=karate_d3$links, labels=karate_d3$nodes, class="hclust")

#dendrogram_hypernyms_verbs_used <- dendro_hypernyms_verbs_used
#attr(dendrogram_hypernyms_verbs_used,"class") <- "dendrogram"
#as.radialNetwork(dendrogram_hypernyms_verbs_used)

## Convert to list format
#Flare <- jsonlite::fromJSON("https://raw.githubusercontent.com/christophergandrud/d3Network/master/JSONdata/flare.json", simplifyDataFrame = FALSE)
#diagonalNetwork(List = Flare) #, fontSize = 10, opacity = 0.9

#require(graphics); require(utils)
#hc <- hclust(dist(USArrests), "ave")
#(dend1 <- as.dendrogram(hc)) # "print()" method

@@

```{r, eval=T, echo=F, results="markup", include=T, message=T, cache=F, ft.arraystretch=0.75}

set_flextable_defaults(fonts_ignore=TRUE)
n_keep=200
verbs_sentence_wordnet_top_ft <-
        verbs_sentence_wordnet_top_unique %>%
        ungroup() %>% 
        head(n_keep) %>%
        dplyr::select(n, lemma, gloss ) %>% #wordnetid
        mutate(gloss=gloss %>% str_replace_all('[^A-Za-z0-9 ,.\"]','')) %>%

        flextable::as_flextable() %>%

        #bg( j = condition, part = "body", bg = "#EFEFEF") %>%
        #width(j = 1, width=1.25) %>%
        #width(j = 2:ncol(lit_review_clean), width=0.25) %>%
        flextable::fontsize(size = 6, part = "all") %>% 
        #rotate(rotation="tbrl",part="header") %>%
        set_header_labels( values = list(lemma = "lemma", wordnetid = "wordnetid", gloss="gloss", n="uses")) %>%
        #align(align = "center", part = "body") %>%
        #align(align = "center", part = "header") %>%
        flextable::padding(padding = 0, part = "all") %>%
        flextable::line_spacing(space = 1, part = "body") %>%
        #ftExtra::colformat_md(j = 1, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
        #fit_to_width(max_width=12) #This is crazy slow
        #flextable::autofit() 
        #set_table_properties(width = 1, layout = "autofit")

      bg( i = which( 1:n_keep %% 2 == 1), part = "body", bg = "#EFEFEF") %>%
      #merge_v(part = "body") %>% 
      flextable::width( j = 1, width=0.3) %>%
      flextable::width( j = 2, width=.75) %>%
      flextable::width( j = 3, width=6) %>%
      #flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
      flextable::padding(padding = 0, part = "body") %>%
      #hline(i=which( actor_agents$Player!=c(actor_agents$Player[2:length(actor_agents$Player)], NA) ), border = fp_border(color="gray", width = 0.25), part = "body")

      #add_header( "IR Player_Pieces"="Citations"

      #            top = TRUE ) %>%
      set_header_labels(
        values = list(
          "uses" = "Count",
          'lemma'='Lemma',
          'gloss'='Gloss'
          ) 
        )

#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html

verbs_sentence_wordnet_top_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/verbs_sentence_wordnet_top_ft.Rds'))
verbs_sentence_wordnet_top_ft

>>>>

---
title: "AppendixVerbTrees.Rmd"
output: html_document
---

```{r, echo=F, messages=F, warnings=F, results='hide', eval=T}

@@

  #Isn't it just one minus the other?
  verbs_sentence_wordnet$distances <- rowSums((glosses_embeddings_expanded-sentences_embeddings_expanded)^2)
  verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/data/verbs_sentence_wordnet.Rds"))

@@

  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/data/verbs_sentence_wordnet.Rds"))

@@

ggsave( filename=paste0(here::here(), "/paper/figures/hypernyms_plot.pdf"), plot=p, height=100,width =32,limitsize = FALSE)

@@

ggsave( filename=paste0(here::here(), "/paper/figures/hypernyms_rooted_plot.pdf"), plot=p_rooted, height=100,width =32,limitsize = FALSE)

@@
